\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools}
\usepackage{enumitem}

\title{On the Integer Equation $6+x^3-y^2+y^2z^2=0$}
\author{}
\date{}

\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}
\newtheorem{remark}{Remark}

\begin{document}
\maketitle

\section*{Problem}
Determine the integer solutions of
\[
6+x^3-y^2+y^2z^2=0.
\]
Equivalently,
\[
x^3+y^2(z^2-1)=-6
\quad\text{or}\quad
y^2(1-z^2)=x^3+6.
\]

\section*{Step 1: Immediate special cases}

\begin{prop}
If $y=0$, there is no integer solution.
\end{prop}
\begin{proof}
Then $x^3=-6$, impossible in $\mathbb Z$.
\end{proof}

\begin{prop}
If $z=\pm1$, there is no integer solution.
\end{prop}
\begin{proof}
If $z^2=1$, the equation becomes again $x^3=-6$, impossible.
\end{proof}

\section*{Step 2: Parity and modular restrictions}

\begin{prop}
$z$ cannot be odd.
\end{prop}
\begin{proof}
Assume $z$ odd. Then $z^2\equiv1\pmod 8$, hence $z^2-1\equiv0\pmod 8$.
Reducing
\[
x^3+y^2(z^2-1)=-6
\]
modulo $8$ gives $x^3\equiv-6\equiv2\pmod 8$.
But cube residues mod $8$ are only $0,1,3,5,7$. Contradiction.
\end{proof}

\begin{prop}
If a solution exists, then $z$ is even, $y$ is odd, and $x\equiv3\pmod 4$.
\end{prop}
\begin{proof}
By the previous proposition, $z$ is even.
Then $z^2\equiv0\pmod4$, so $z^2-1\equiv3\pmod4$. Reduce
\[
x^3+y^2(z^2-1)=-6
\]
modulo $4$:
\[
x^3+3y^2\equiv2\pmod4.
\]
If $y$ were even, then $3y^2\equiv0\pmod4$, so $x^3\equiv2\pmod4$, impossible.
Hence $y$ is odd, so $y^2\equiv1\pmod4$, giving $x^3\equiv3\pmod4$, thus $x\equiv3\pmod4$.
\end{proof}

\section*{Step 3: The case $z=0$}

\begin{prop}
There is no integer solution with $z=0$.
\end{prop}
\begin{proof}
If $z=0$, the equation is
\[
y^2=x^3+6.
\]
This is the Mordell curve $E:\ y^2=x^3+6$.

To determine all integral points on $E$, one may use the standard
elliptic-curve integral-point algorithm (Baker bounds + elliptic logarithms),
implemented in SageMath:
\[
\texttt{EllipticCurve([0,0,0,0,6]).integral\_points()}.
\]
Running this computation returns the empty set:
\[
E(\mathbb Z)=\varnothing.
\]
Hence no integer pair $(x,y)$ satisfies $y^2=x^3+6$, so no solution exists with $z=0$.
\end{proof}

\section*{What is fully proved, and what remains}

All of the following are now proved:
\begin{itemize}[leftmargin=2em]
\item no solutions with $y=0$;
\item no solutions with $z=\pm1$;
\item no solutions with odd $z$;
\item no solutions with $z=0$.
\end{itemize}

Therefore any possible solution would have to satisfy
\[
z\in2\mathbb Z\setminus\{0\},\qquad y\equiv1\pmod2,\qquad x\equiv3\pmod4.
\]

\begin{remark}
At this stage, a complete elimination of the remaining branch
$z\in2\mathbb Z\setminus\{0\}$ has not been established in this write-up.
So this document gives a fully rigorous reduction plus complete resolution
of all listed special cases, but not yet a full global classification.
\end{remark}

\section*{Sanity checks}

\subsection*{(A) Substitution checks for all candidate special cases}
\begin{itemize}[leftmargin=2em]
\item $y=0$ forces $x^3=-6$ (not an integer cube), so no candidate survives.
\item $z=\pm1$ forces $x^3=-6$, so no candidate survives.
\item $z=0$ reduces to $y^2=x^3+6$, and the integral-point computation gives no candidate.
\end{itemize}

\subsection*{(B) Wide bounded search (evidence only)}
A direct search over
\[
|x|\le 200,\quad |y|\le 200,\quad |z|\le 50
\]
finds no solution. Extending to
\[
|y|\le 3000,\quad |z|\le 3000
\]
with exact-cube checking for $x^3=-6-y^2(z^2-1)$ also finds none.
This supports nonexistence but is not a proof for all integers.

\section*{Concise theorem statement and summary}

\begin{thm}[Proved nonexistence in all listed special branches]
For
\[
6+x^3-y^2+y^2z^2=0,\qquad x,y,z\in\mathbb Z,
\]
there are no solutions in each of the branches
\[
y=0,\quad z=\pm1,\quad z\ \text{odd},\quad z=0.
\]
Hence any hypothetical solution must satisfy
\[
z\in2\mathbb Z\setminus\{0\},\ y\ \text{odd},\ x\equiv3\pmod4.
\]
\end{thm}

\noindent\textbf{Proof summary.}
Rewrite as $x^3+y^2(z^2-1)=-6$. Immediate substitutions eliminate
$y=0$ and $z=\pm1$. Modulo $8$, odd $z$ is impossible since it would force
$x^3\equiv2\pmod8$. For even $z$, modulo $4$ forces $y$ odd and $x\equiv3\pmod4$.
Finally, $z=0$ gives the Mordell curve $y^2=x^3+6$, whose integral points are empty.
Therefore all these branches are impossible.

\end{document}
